---
title: "More ggplot Figures Peer Review"
output:
  pdf_document: default
  html_document: default
---

# PUT YOUR NAME HERE: Minh Tri Bui

## Problem 1

Create the figure in the solution for Problem 1, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
library(tidyverse)

set.seed(12345)
var1<-runif(50,0,10)
set.seed(12345)
var2<-var1+rnorm(50,5,2)
set.seed(12345)
var3<- var1*(-rnorm(50,1,.2))

dat1<-tibble(var1,var2,var3)


```

```{r problem_1,echo=FALSE,message=FALSE}

ggplot(dat1, aes(x=var1,y=var2))+
  geom_point()+
  geom_smooth(method = 'loess') +
  labs(x = "Variable 1" , y= "Variable 2")
```

## Problem 2

Create the figure in the solution for Problem 2, using the data included in the R Markdown file.

```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(10)
var1<-runif(50,0,10)
set.seed(10)
var2<-var1+rnorm(50,5,2)
set.seed(10)
var3<- var1*(-rnorm(50,1,.2))

dat2<-tibble(var1,var2,var3)
```


```{r solution_p2,echo=FALSE,message=FALSE}
library(GGally)

# custom function for density plot
my_density <- function(data, mapping, ...){
  ggplot(data = data, mapping = mapping) + 
    geom_density(alpha = 0.5,
                 fill = "Blue", ...)
}

# custom function for scatterplot
my_scatter <- function(data, mapping, ...){
  ggplot(data = data, mapping = mapping) + 
    geom_point(alpha = 0.5,
               color = "orange")  
}


# create scatterplot matrix
ggpairs(dat2, 
        lower=list(continuous = my_scatter), 
        diag = list(continuous = my_density)) +
  theme_bw()

```

## Problem 3

Create the figure in the solution for Problem 3, using the data included in the R Markdown file.

```{r problem_3_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(12)
var1<-runif(50,0,10)
set.seed(12)
var2<-var1+rnorm(50,5,2)
set.seed(12)
var3<- var1*(-rnorm(50,1,.2))

dat3<-tibble(var1,var2,var3)
```

```{r problem3,echo=FALSE}
library(ggcorrplot)
r <- cor(dat3,use="complete.obs")
ggcorrplot(r, hc.order = FALSE, type = "lower", title = "Correlations") 

```

## Problem 4

Create the figure in the solution for Problem 4, using the data included in the R Markdown file.

```{r problem_4_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(5678)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat4<-tibble(names,var1)
```

```{r problem_4,echo=FALSE}
ggplot(dat4, aes(var1, reorder(names, var1))) +
  geom_point(size = 5) +  # Use a larger dot
  labs(x = "Variable 1", y = "")+
  theme_gray(base_size = 14)+
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_line(colour = "red", linetype = "dashed")  )


```

## Problem 5

Create the figure in the solution for Problem 5, using the data included in the R Markdown file.

```{r problem_5_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(13)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat5<-tibble(names,var1)
```

```{r problem_5,echo=FALSE}

ggplot(dat5, aes(var1, reorder(names, var1))) +
  geom_segment(aes(yend = names), xend = 0, colour = "forestgreen") +
  lims(x = c(0,35)) +
  geom_point(size = 2) +  # Use a smaller dot
  labs(x = "Variable 1", y = "")+
  theme_gray(base_size = 10)+
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.x = element_text(angle = 90, hjust = 1)
      )+
  coord_flip()

```

## Problem 6

Create the figure in the solution for Problem 6, using the data included in the R Markdown file.

```{r problem_6_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(8)
fiction<-tibble(Genre=rep("Fiction",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(7)
biography<-tibble(Genre=rep("Biography",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(9)
mystery<-tibble(Genre=rep("Mystery",5),Time=seq(1:5),Total=sample(1:10,5))

books_checked_out<-bind_rows(fiction,biography,mystery)
```

```{r problem_6,echo=FALSE}
ggplot(books_checked_out, aes(x = Time , y = Total, fill = Genre)) +
  geom_area() 

```

## Problem 7

Create the figure in the solution for Problem 7, using the data included in the R Markdown file.

```{r problem_7_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

books_checked_out2 <- books_checked_out %>%
  filter(Time==1 | Time==5) %>%
  pivot_wider(names_from = Time,values_from=Total) %>%
  rename(Time1=`1`,Time5=`5`)
```
   
```{r,problem_7,echo=FALSE,message=FALSE}   
library(ggalt)
library(tidyr)
library(dplyr)
ggplot(books_checked_out2, aes(y = reorder(Genre,Time1),
                          x = Time1,
                          xend = Time5)) +  
  geom_dumbbell(size_x = 3, 
                size_xend = 3,  
                colour = "black", 
                colour_x = "red", 
                colour_xend = "purple") +
  labs( x= "", y = "Genre")
```

## Problem 8

Create the figure in the solution for Problem 8, using the data included in the R Markdown file.

```{r, problem_8_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

pie_dat<-c(1,2,3,4,5)
```

```{r, problem_8,echo=FALSE}


###HINT: check the Help file for pie to see how to specify the color to the my_color palette

library(RColorBrewer)

my_color<-brewer.pal(5,"Spectral")

pie(pie_dat ,  col=my_color )

```


